%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \eduentry
    {Developed backend ML APIs for \href{https://www.chararu.jp/}{Chararu}.} % Role
    {Software Engineer at rinna Co., Ltd.} % Corp.
    {Tokyo, Japan} % Location
    {Jun. 2021 - Jan.  2023} % Date(s)
%---------------------------------------------------------
  \eduentry
    {Research routing and spectrum assignment using reinforcement learning for optical networks. } % Role
    {Researcher at NTT Network Innovation Laboratories} % Corp.
    {Yokosuka, Japan} % Location
    {Apr. 2020 - Jun. 2021} % Date(s)
%---------------------------------------------------------
  \eduentry
    {Researched fine-grained dataflow accelerator for CNN Inference. } % Role
    {Intern at Preferred Networks Inc.} % Corp.
    {Tokyo, Japan} % Location
    {Aug. 2019 - Sep. 2019} % Date(s)
%---------------------------------------------------------
  \eduentry
    {Developed an FPGA-based accelerator for a proprietary neural network model, and contributed to the open-source project \href{https://github.com/sony/nnabla}{Neural Network Libraries. }} % Role
    {Intern at SONY Corp.} % Corp.
    {Tokyo, Japan} % Location
    {Aug. 2018 - Sep. 2018} % Date(s)
%---------------------------------------------------------
  \eduentry
    {Contributed to the open-source project \href{https://github.com/HirokiNakahara/GUINNESS}{GUINNESS. }} % Role
    {Research Assistant at Nakahara Lab,\ Tokyo Institute of Technology} 
    {Tokyo, Japan} % Location
    {Apr. 2017 - Mar. 2020} % Date(s)
%---------------------------------------------------------
  \eduentry
    {Developed crawler(Python) and in-house system(Javascript(JQuery), JAVA(Spring)), and Conducted landing page optimization(Python(scikit-learn))} % Role
    {Intern at So-net Media Networks Co.,Ltd. (SMN Corporation)} % Corp.
    {Tokyo, Japan} % Location
    {Nov. 2016 - Mar. 2018} % Date(s)
%---------------------------------------------------------
  \eduentry
    {Designed and developed the backend API for the application \href{https://apps.apple.com/jp/app/id1016332071?l=en}{shinkuru} by using Typescript with both domain driven design and clean architecture.} % Role
    {Intern at Fringe81 Inc. (Unipos Inc.)} % Corp.
    {Tokyo, Japan} % Location
    {Aug. 2016 - Sep. 2016} % Date(s)
%---------------------------------------------------------
\end{cventries}
