
\begin{publication}
\item \publicationstyle{{\bfseries Masayuki Shimoda}, Atsushi Takahashi: Gridless Gap Channel Routing to Minimize Wirelength, IPSJ Trans. on System LSI Design Methodology, Vol.18, 2025.} \href{}{ \entrytitlestyle{[URL]}}.



\item \publicationstyle{Zezhong Wang,{\bfseries Masayuki Shimoda}, Atsushi Takahashi: SDG channel routing to minimize wirelength for generalized channel, IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences, Communications and Computer Sciences, 2025.}.


\item \publicationstyle{{\bfseries Masayuki Shimoda}, Atsushi Takahashi: Gridless gap channel routing with variable-width wires, IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences, 2024.} \href{https://doi.org/10.1587/transfun.2024VLP0003}{ \entrytitlestyle{[URL]}}.

\item \publicationstyle{Takafumi Tanaka,{\bfseries Masayuki Shimoda}: Pre- and post-processing techniques for reinforcement-learning-based routing and spectrum assignment in elastic optical networks, J. Opt. Commun. Netw.  15, 1019-1029, 2023} \href{https://doi.org/10.1364/JOCN.503599}{ \entrytitlestyle{[URL]}}.

\item \publicationstyle{(Invited){\bfseries Masayuki Shimoda},Youki Sada,Hiroki Nakahara: FPGA-based Inter-layer Pipelined Accelerators for Filter-wise Weight-balanced Sparse Fully Convolutional Networks with Overlapped Tiling, J Sign Process Syst, 1-14, 2021} \href{http://link.springer.com/article/10.1007/s11265-021-01642-6}{ \entrytitlestyle{[URL]}}.

\item \publicationstyle{{\bfseries Masayuki Shimoda},Youki Sada,Ryosuke Kuramochi,Shimpei Sato,Hiroki Nakahara: SENTEI: Filter-wise Pruning with Distillation Towards Efficient Sparse Convolutional Neural Network Accelerators, IEICE Transactions, Vol.E103-D, pp.2463-2470, 2020}\href{https://search.ieice.org/bin/summary.php?id=e103-d_12_2463&category=D&year=2020&lang=E&abst=}{ \entrytitlestyle{[URL]}}.

\item \publicationstyle{Hiroki Nakahara,Haruyoshi Yonekawa,Tomoya Fujii,{\bfseries Masayuki Shimoda},Shimpei Sato: GUINNESS: A GUI Based Binarized Deep Neural Network Framework for Software Programmers, IEICE Transactions, Vol.E102-D, pp.1003-1011,  2019} \href{http://search.ieice.org/bin/summary.php?id=e102-d_5_1003}{ \entrytitlestyle{[URL]}}.

\item \publicationstyle{{\bfseries Masayuki Shimoda},Shimpei Sato,Hiroki Nakahara: Power Efficient Object Detector with an Event-Driven Camera for Moving Object Surveillance on an FPGA, IEICE Transactions, Vol.E102-D, pp.1020-1028,  2019} \href{http://search.ieice.org/bin/summary.php?id=e102-d_5_1020}{ \entrytitlestyle{[URL]}}.

\item \publicationstyle{Koji Obokata, Genki Oniyanagi, Kenta Sato, {\bfseries Masayuki Shimoda},Hiroki Chiba: Development of a Consensus Building System to Support Community Planning that Centers on Information Sharing Using the Map, Theory and applications of GIS, vol. 24, no. 2, pp. 115–124, 2016 (in Japanese)}\href{https://www.jstage.jst.go.jp/article/thagis/24/2/24_115/_article/-char/ja/}{ \entrytitlestyle{[URL]}}.

\end{publication}
